The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-10 analysis/paper/paper.qmd
Update analysis/paper/paper.qmd

# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value, fill = document), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")

>>>>

# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value, fill = document), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")
